LC-MS ^13^C Lactate Measurements

### 2022-12-19 analysis/glc6-lactate.qmd
generate standard curve plots for flux data

```{r}
#| label: qbias-corr

se_drift |> 
  dplyr::filter(type != "qc")
```

@@

se_drift |> 
  dplyr::filter(type == "std" & metabolite == "LAC M0") |> 
  dplyr::mutate(conc = as.numeric(conc)) |> 
  ggplot() +
  aes(
    x = conc, 
    y = area
  ) +
  geom_point()
```

@@

se_drift |> 
  filter(type == "sample") |> 
  filter(metabolite == "LAC M3") |> 
  left_join(pheno, by = "number") |> 
  group_by(date, oxygen, time) |> 
  wmo::remove_nested_outliers(area, remove = TRUE) |> 
  summarize(area = mean(area)) |> 
  ggplot() +
  aes(
    x = time, 
    y = area, 
    color = oxygen
  ) +
  geom_point() +
  stat_summary(
    geom = "line"
  )
```

>>>>

@@

df_drift |> 
  dplyr::filter(type == "std" & metabolite == "LAC M0") |> 
  dplyr::mutate(conc = as.numeric(conc)) |> 
  ggplot() +
  aes(
    x = conc, 
    y = area
  ) +
  geom_point()
```

@@

df_drift |> 
  filter(type %in% letters[1:3]) |> 
  filter(metabolite == "LAC M0") |> 
  left_join(pheno, by = "number") |> 
  group_by(type, oxygen, time) |> 
  wmo::remove_nested_outliers(area, remove = TRUE) |> 
  summarize(area = mean(area)) |> 
  ggplot() +
  aes(
    x = time, 
    y = area, 
    color = oxygen
  ) +
  geom_point() +
  stat_summary(
    geom = "line"
  )
```
